---
title: "Housing Prices"
author: "Gardenian in blossom"
date: "`r Sys.Date()`"
highlight-style: pygments # 代码块语法高亮风格
toc: true # 添加目录导航
number-sections: true # 给各部分家序号
format: 
  html:
    code-fold: true
    html-math-method: katex
  pdf:
    geometry: 
      - top = 30mm
      - left = 30mm
    code-line-numbers: true # 给代码添加行号显示
    documentclass: ctexart
    latex-engine: xelatex
  docx: default
bibliography: references.bib
---

## Introduction

In this analysis, we build a model predicting sale prices of houses based on data on houses that were sold in the Duke Forest neighborhood of Durham, NC around November 2020. Let's start by loading the packages we'll use for the analysis.

```{r}
#| label: load-pkgs
#| code-summary: "Packages"
#| message: false

library(openintro)  # for data
library(tidyverse)  # for data wrangling and visualization
library(knitr)      # for tables
library(broom)      # for model summary
```

We present the results of exploratory data analysis in @sec-eda and the regression model in @sec-model.

<!--# ADD CITATION HERE -->

## Exploratory data analysis {#sec-eda}

The data contains `{r} nrow(duke_forest)` houses. As part of the exploratory analysis let's visualize and summarize the relationship between areas and prices of these houses.

### Data visualization

@fig-histogram shows two histograms displaying the distributions of `price` and `area` individually.

```{r}
#| label: fig-histogram
#| fig-cap: "Histograms of individual variables"
#| fig-subcap:
#|   - "Histogram of `price`s"
#|   - "Histogram of `area`s" 
#| layout-ncol: 2

ggplot(duke_forest, aes(x = price)) +
  geom_histogram(binwidth = 50000) +
  labs(title = "Histogram of prices")

ggplot(duke_forest, aes(x = area)) +
  geom_histogram(binwidth = 250) +
  labs(title = "Histogram of areas")
```

@fig-scatterplot displays the relationship between these two variables in a scatterplot.

```{r}
#| label: fig-scatterplot
#| fig-cap: "Scatterplot of price vs. area of houses in Duke Forest"

ggplot(duke_forest, aes(x = area, y = price)) +
  geom_point() +
  labs(title = "Price and area of houses in Duke Forest")
```

### Summary statistics

@tbl-stats displays basic summary statistics for these two variables.

```{r}
#| label: tbl-stats
#| tbl-cap: "Summary statistics for price and area of houses in Duke Forest"

duke_forest %>%
  summarise(
    `Median price` = median(price),
    `IQR price` = IQR(price),
    `Median area` = median(area),
    `IQR area` = IQR(area),
    `Correlation, r` = cor(price, area)
    ) %>%
  kable(digits = c(0, 0, 0, 0, 2))
```

## Modeling {#sec-model}

@eq-gougu 是勾股定理的表达式

We can fit a simple linear regression model of the form shown in @eq-slr.

\[ADD EQUATION HERE\]

插入数学公式，/mat，会弹出提示

$$
x^2 + y^2 = z^2
$$ {#eq-gougu}

$$
price = \hat{\beta}_0 + \hat{\beta}_1 \times area + \epsilon
$$ {#eq-slr}

@tbl-lm shows the regression output for this model.

```{r}
#| label: tbl-lm
#| tbl-cap: "Linear regression model for predicting price from area"

price_fit <- lm(price ~ area, data = duke_forest)
  
price_fit %>%
  tidy() %>%
  kable(digits = c(0, 0, 2, 2, 2))
```

Today, I read the article "The X-Age Project to construct a Chinese aging clock."[@li2025]

::: callout-note
This is a pretty incomplete analysis, but hopefully the document provides a good overview of some of the authoring features of Quarto!
:::

::: callout-tip
this is a tip.
:::

::: callout-important
this is an important message.
:::

::: callout-caution
be cautious please.
:::

::: callout-warning
this is a warning.
:::

## References
